### 2017-07-19 introduction.tex
software -> infrastructure and services

To address these concerns, myriad computational infrastructures
have been developed. These infrastructures, including \NAMENS \cite{babuji2016cloud},
implement the software required to securely store and analyze protected
data. However, in almost every case, there is one significant weakness to these systems: the individual humans tasked with administering and managing
data collections are fallible and prone to error. Most often, the policies and processes for managing
the data are ad hoc and lack software support.

>>>>

To address these concerns, myriad computational infrastructures
have been developed. These infrastructures, including \NAMENS \cite{babuji2016cloud},
implement the infrastructure and services required to securely store and analyze protected
data. However, in almost every case, there is one significant weakness to these systems: the individual humans tasked with administering and managing
data collections are fallible and prone to error. Most often, the policies and processes for managing
the data are ad hoc and lack software support.
